---
title: '**Norway’s economy and its impact on the country**'
author: "Victor Dépré / Skema Business School student"
date: "07/16/2020"
output:
  html_document:
    toc: 2
  pdf_document:
    toc: 2 
---
<style>
.html-widget {margin: auto;}
</style>
<style>
body {text-align: justify}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


---

# **Introduction**

---

Norway is a very interesting country that is quite exemplary and could inspire many other countries in economic, social and especially environmental terms.

* Historically, Norway has long been one of the poorest countries in Europe, but the very interesting development of this country has made it today a rich country with a very high standard of living and well-being. With an HDI of 0.954 in 2018, Norway defies all competition and is in pole position worldwide. Add to this the ecological awareness of its citizens, which has made Norway one of the precursors of the ecological transition and we have a country that is more than exemplary, both economically and socially as well as environmentally.

* Norway’s economy, since the beginning of the industrial revolution, has shown solid growth. The transport of goods is an important part of Norway’s exports, but economic growth is also largely due to the abundance of natural resources in the country such as oil and hydroelectricity. The exploitation of its oil resources accounts for half of the total value of its exports. Agriculture and heavy industry are declining relative to the service and oil sectors. Moreover, its public sector is one of the largest in the world in relation to its GDP.

* On top of that Norway is a very environmentally committed country. For example, last June Norway announced that the sale of petrol cars would be banned by 2025. The country is already among the European countries offering the most tax incentives for buying electric cars. Norway has also become the first country to ban deforestation. Public procurement will now have to exclude any offer from a company whose products may have contributed to deforestation. The Norwegian Parliament has announced that the country will aim for carbon neutrality by 2030, 20 years ahead of the target of reducing net greenhouse gas emissions, which are responsible for global warming, to zero and nearly all of the country’s electricity production is already clean, since it is hydroelectric.


**Outline**

* **Part 1** : An unusual economy.

* **Part 2** : Its impact on the social area.

* **Part 3** : A pioneering country in terms of ecology .

* **Part 4** : An unevenly distributed population.


---------------

# **An unusual economy**

--------------------

Norway's economy, although sensitive to economic cycles, has shown robust growth since the beginning of the industrial revolution. Freight transport is a strong constant in Norway's exports, but economic growth is largely due to the abundance of natural resources, including oil, hydroelectricity and fisheries. Indeed, the exploitation of its oil resources accounts for half of the total value of its exports. Agriculture and heavy industry are declining relative to the service and oil sectors. Its public sector is one of the largest in the world in relation to its gross domestic product.

Norway is characterised by a very high standard of material living and is performing well on aspects like well-being, thanks to the conjunction of abundant natural resources, well-designed public policies and social values based on inclusion and egalitarianism, illustrated in particular by the fact that the authorities are working hard to actively to remove barriers to women's careers. Nevertheless, the significant drop in oil prices in 2014 recalls that Norway is exposed to external risks and, and social values based on inclusion and egalitarianism, illustrated in particular by the fact that the authorities are working hard to remove barriers to women's careers.
Nevertheless, the significant drop in oil prices in 2014 recalls that Norway is exposed to external risks. Therefore, stresses the importance of flexibility and the competitiveness of the continental economy. The growth of property prices remain strong in Norway, which raises concerns about its macroeconomic stability.

---------------

**Summary**

* **Norway's main business sectors.**

* **Norway's trade balance.**

* **Gdp per fylker map.**

* **Norway's ranking considering the Index of economical freedom.**

* **Detail of the Index of economical freedom.**

---------------

## Norway's main business sectors

---------------

Exploitation of Norway’s vast oil and gas reserves has been far and away the biggest contributor to the Norwegian economy since they were first discovered in the 1960s. The country generates almost 98% of its electricity from hydropower so most of the oil and gas is exported overseas and that's why it represents around 20% of Norway's economy as can be seen on the graph.

One of the challenges for the Norwegian government will be how to manage the economic transition after the depletion of oil and gas resources. There are still huge reserves in the Barents Sea, but they are located in the Arctic Circle, which means that access to them is considered more difficult and more dangerous for the environment.

```{r include=FALSE}
library(ggplot2)
library(plotly)

PNBperCategory <- data.frame(
  stringsAsFactors = FALSE,
  Category=c("Agriculture", "Forest", "Fisheries and aquaculture", "Oil and Gas Development", "Mining extraction", "Industry", "Power supply", "Construction and public works", "Commerce", "Hotels and Restaurants", "Transport in pipes", "Other transports", "Post and telecoms", "Maritime trade", "Banking and Insurance", "Real Estate Services", "Business Services", "Services to the private sector", "Delivery of Public Management Services", "Correction Posts "),
  Score=c(0.6, 0.3, 0.5, 19.8	, 0.2	, 9.2, 2	, 4, 7.9, 1.2, 1.2, 2.7, 1.8, 1.7, 3.3, 5, 8.7, 4.7	, 15.6, 9.7))

PNBperCategory$Category <- with(PNBperCategory, reorder(Category, +Score))

PNBperCategory1 <- ggplot(PNBperCategory, 
            aes(x = Category, y = Score, color = Score, label = Score)) +
  geom_col(aes(fill = Score)) +
  ggtitle("% of GNP per category") + 
  xlab("Country") + ylab("% of GNP") + 
  coord_flip() +
  labs(caption = "Source: www.heritage.org") +
  scale_fill_distiller(palette = "Set2", trans = "reverse") +
  scale_color_distiller(palette = "Set2", trans = "reverse") +
  theme(legend.position = "none") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text = element_text(size = 7), 
  panel.background = element_rect(fill = "gray98")) +labs(caption = NULL)
  
DynagraphPNBPC <- ggplotly(PNBperCategory1)

```

```{r echo=FALSE}

DynagraphPNBPC
  
```

---------------

## Norways Trade Balance

---------------


The balance of trade in goods and services is the difference between exports of goods and services and imports of goods and services, expressed in dollars. A positive balance indicates that exports exceed imports in value (trade surplus). A negative balance, on the contrary, indicates that imports exceed exports in value (trade deficit). The statistics relate this balance to the size of economic activity (GDP). We can see on the graph below that the trade balance reached its maximum in 2008 before the crisis. The crisis has had an important impact on the country's exports since 2008 : exports have almost only fallen except in 2011 and 2012 thanks to the return of oil exports.

The increase in the trade balance in 2017 and 2018 is explained by the appreciation of the price of Brent oil prices in 2017. It is also due to the good health of manufactured products, which enabled exports to grow by around 12% compared to 2016.

```{r include=FALSE}
library(WDI)
library(ggplot2)
library(plotly)

TB <- WDI(indicator = "NE.RSB.GNFS.CD", country = c("NOR"), start = 1970, end = 2020)
TB

graphTB <- ggplot(TB) +
 aes(x = year, y = NE.RSB.GNFS.CD, fill = country) +
 geom_area(size = 1L) +
 scale_fill_brewer(palette = "PuOr") +
 labs(y = "dollars", title = "Norway's trade balance (in $)") +
 theme_minimal() +
 theme(legend.position = "none")

DynagraphTB <- ggplotly(graphTB)

```


```{r echo=FALSE}

DynagraphTB

```

---------------

## GDP Map

---------------


This is a map showing the GDP per region in Norway, it is immediately noticeable that the economy is concentrated in southern Norway. Moreover, the 4 regions with the highest GDP, Oslo, Akershus, Hordaland and Rogaland alone account for half of the country's GDP, which is around 300 billion euros. 

This makes Norway a country with a very asymmetrical economy, which leads to unequal living standards between south and north. This imbalance can be easily seen on the unemployment map further bellow.

```{r warning=TRUE, include=FALSE}

library(sf)
library(ggplot2)
library(tmap)
library(tmaptools)
library(leaflet)
library(dplyr)

mydatabis <- readr::read_csv("Gdp Map/GDPperFylker.csv")

mymapbis <- st_read("Gdp Map/NORWAY SHAPE BIS/NOR_adm1.shp", stringsAsFactors = FALSE)

datamap1bis <- inner_join(mymapbis, mydatabis) 


```

```{r warning=FALSE, include=FALSE}

tm_shape(datamap1bis) +
  tm_polygons("GDP, millions of euro", id = "NAME_1", palette = "Greens")+ "GDP"
  theme_minimal()
  
tmap_mode("view")
GdpMap <- tmap_last()

```

```{r echo=FALSE, warning=FALSE}

GdpMap

#tmap_save(GdpMap, "GdpMap.html")

```

---------------

## Norway's ranking considering the Index of Economic Freedom 

---------------

Economic freedom is the fundamental right of every human to control his or her own labor and property. In an economically free society, individuals are free to work, produce, consume, and invest in any way they please. In economically free societies, governments allow labor, capital, and goods to move freely, and refrain from coercion or constraint of liberty beyond the extent necessary to protect and maintain liberty itself.

Norway’s economic freedom score is 73.4, making its economy the 28th freest in the 2020 Index. Its overall score has increased by 0.4 point due to a higher labor freedom score. Norway is ranked 15th among 45 countries in the Europe region, and its overall score is well above the regional and world averages.

```{r include=FALSE}

IndexEcoFreeRanking <- data.frame(
  stringsAsFactors = FALSE,
  Category=c("Singapore", "Hong Kong", "New Zealandy", "Australia", "Switzerland", "Ireland", "United Kingdom", "Denmark", "Canada", "Estonia", "Taiwan", "Georgia", "Iceland", "Netherlands", "Chile", "Lithuania", "United States", "United Arab Emirates", "Luxembourg", "Finland ", "Mauritius", "Sweden", "Czech Republic", "Malaysia", "South Korea", "Israel", "Germany", "Norway", "Austria", "Japan"),
  Score=c(89.4	, 89.1, 84.1, 82.6	, 82.0	, 80.9, 79.3	, 78.3, 78.2, 77.7, 77.1, 77.1, 77.1, 77.0, 76.8, 76.7, 76.6, 76.2	, 75.8, 75.7, 74.9, 74.9, 74.8, 74.7	, 74.0, 74.0, 73.5, 73.4, 73.3, 73.3)) 

IndexEcoFreeRanking$Category <- with(IndexEcoFreeRanking, reorder(Category, +Score))

IndexEcoFreeRanking1 <- ggplot(IndexEcoFreeRanking, 
            aes(x = Category, y = Score, color = Score, label = Score)) +
  geom_col(aes(fill = Score)) +
  ggtitle("Ranking average scores") + 
  xlab("Country") + ylab("Score") + 
  coord_flip() +
  labs(caption = "Source: www.heritage.org") +
  scale_fill_distiller(palette = "Oranges", trans = "reverse") +
  scale_color_distiller(palette = "Oranges", trans = "reverse") +
  theme(legend.position = "none") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text = element_text(size = 7), 
  panel.background = element_rect(fill = "gray98")) +labs(caption = NULL)
  
DynagraphRK <- ggplotly(IndexEcoFreeRanking1)

```

```{r echo=FALSE}

DynagraphRK
  
```

---------------

## Detail of the Index of Economic Freedom

---------------

It can be seen from the graph below that overall Norway has very high scores, especially with regard to the integrity of the government. Nevertheless the greatest impediment to greater economic freedom in Norway is too much government spending. Reducing it will be difficult, however, because a large part of the economy and an even larger percentage of the government’s budget are structured around revenue from Equinor, a state-owned oil, gas, and wind-energy company.

```{r include=FALSE}

library(plotly)

IndexEcoFree <- data.frame(
  stringsAsFactors = FALSE,
  Category=c("Property Rights", "Judical Effectiveness", "Government Integrity", "Tax Burden", "Government Spending", "Fiscal Health", "Business Freedom", "Labor Freedom", "Monetary Freedom", "Trade Freedom", "Investment Freedom", "Financial Freedom"),
  Score=c(84.3,	82.8,	95.6,	57.7,	25.6,	86.1,	57.4,	86.7,	74.8,	83.8,	75,	60))

IndexEcoFree$Category <- with(IndexEcoFree, reorder(Category, +Score))

IndexEcoFree1 <- ggplot(IndexEcoFree, 
            aes(x = Category, y = Score, color = Score, label = Score)) +
  geom_col(aes(fill = Score)) +
  ggtitle("Index of Economic Freedom, 2020") + 
  xlab("Category") + ylab("Score") + 
  coord_flip() +
  labs(caption = "Source: www.heritage.org") +
  scale_fill_distiller(palette = "Oranges", trans = "reverse") +
  scale_color_distiller(palette = "Oranges", trans = "reverse") +
  theme(legend.position = "none") + 
  theme(panel.background = element_rect(fill = "gray98")) +
  theme(plot.title = element_text(hjust = 0.5))
  
DynagraphEF <- ggplotly(IndexEcoFree1)

```

```{r echo=FALSE}

DynagraphEF
  
```

---------------

# **Impact on the social area**

--------------------

Norwegian values are rooted in egalitarian ideals. Most Norwegians believe in equal distribution of wealth and that everyone should have equal opportunities. Norwegians generally have a high degree of trust in the government and believe in the welfare state. Norway is called a welfare state because the government, both federal and local, has primary responsibility for the welfare of its citizens. The Norwegian welfare state is mainly financed by taxes and duties paid by its inhabitants. Norway is ranked as one of the best countries to live in and has one of the lowest crime rates in the world.

Norway is definitely a part of Europe, but is not a member of the EU. However, the country is fully integrated in the European community in everything from trade and economy, through the European Economic Area (EEA) agreement, to education and research – for instance through the Erasmus programme. Norway also participates in the Schengen agreement, making travelling to and from other Schengen countries easy.

---------------

**Summary**

* **Wellbeing.**

* **Unemployment map.**

* **Health and wellness.**

* **Political rights.**

---------------

## Well-being

---------------

Relative to other high-income countries, Norway performs extremely well across various indicators of resident's well-being. Life expectancy at birth has increased by two years since 2005, and average life expectancy is now two years higher than the average for OECD countries. This position is in contrast to the United States, which has a life expectancy not as good as Norway and that's the reason why Norway is above the United States or countries like Finland or Germany. On this graph we can also see that well-being in China is rather low compared to other countries (mainly because of the insecurity and stress omnipresent in the population), but this is still correct compared to countries like South Sudan which is the country where well-being indicators are the lowest in the world.

```{r, include=FALSE}
library(spiR)

FOW <- sqs_spi_data(country = c("AUS", "DNK", "NOR", "NLD", "DEU", "FIN", "SSD","FRA","CHN","USA"), 
                       year = c("2014","2015","2016", "2017", "2018", "2019"), 
                       indicators = "FOW")
```

```{r, include=FALSE}

library(ggplot2)
library(plotly)

graph <- ggplot(FOW) +
 aes(x = var_year, y = value, colour = countryName, group = countryName) +
 geom_line(size = 1.2) +
 scale_color_hue() +
 labs(x = "Year", y = "Well-being Indicator", title = "Well-being", color = "Countries") +
 theme_minimal() +
 theme(axis.text.y = element_text(size = 5))

graph1 <- ggplotly(graph)
graph1

```

```{r echo=FALSE}
graph1
```

---------------

## Unemployment Map

---------------

This map shows the unemployment rate in each Norwegian region. It shows that the share of the unemployed in the Norwegian labour force is very low (average 3.7%), especially since the regions with the highest rate are the least dense (see Density map). Moreover, according to International Monetary Fund estimates, the unemployment rate in Norway is expected to stabilise at 3.7% from 2020 onwards which is really good. 

There are two reasons for such a low unemployment rate: firstly, the country invests part of its oil revenues in a fund that it can use in times of crisis, and secondly, as Norway belongs neither to the euro zone nor to the European Union, it is not subject to the constraints of debt reduction. 

```{r warning=FALSE, include=FALSE}

library(sf)
library(ggplot2)
library(tmap)
library(tmaptools)
library(leaflet)
library(dplyr)

mydatabisbisbis <- readr::read_csv("Unemployment Map/Unemployment per Fylker.csv")

mymapbisbisbis <- st_read("Unemployment Map/NORWAY SHAPE BIS BIS BIS/NOR_adm1.shp", stringsAsFactors = FALSE)

datamap1bisbisbis <- inner_join(mymapbisbisbis, mydatabisbisbis) 


```

```{r warning=FALSE, include=FALSE}

tm_shape(datamap1bisbisbis) +
  tm_polygons("Unemployment rate, %", id = "NAME_1", palette = "Purples")+ "Unemployment rate, %"
  theme_minimal()
  
tmap_mode("view")
UnemploymentMap <- tmap_last()

```

```{r echo=FALSE, warning=FALSE}

UnemploymentMap

#tmap_save(UnemploymentMap, "UnemploymentMap.html")

```

---------------

## Health and Wellness

---------------

In Norway, all hospitals are funded by the public as part of the national budget. However, while medical treatment is free of charge for any person younger than the age of sixteen, residents who have reached adulthood must pay a deductible each year before becoming eligible for an exemption card. The card entitles one to free healthcare for the remainder of that year.

All public hospitals in Norway are run by four Regional Health Authorities overseen by the Ministry of Health and Care Services. In addition to these public hospitals, there are a small number of privately owned health clinics currently operating.

```{r, include=FALSE}

library(spiR)

HWE <- sqs_spi_data(country = c("AUS", "DNK", "NOR", "NLD", "DEU", "SWE", "ESP", "FRA"), 
                       year = c("2014","2015","2016", "2017", "2018", "2019"), 
                       indicators = "HWE")

```

```{r, include=FALSE}

library(ggplot2)
library(plotly)

graph2 <- ggplot(HWE) +
 aes(x = var_year, y = value, colour = countryName, group = countryName) +
 geom_line(size = 1.2) +
 scale_color_hue() + 
 labs(x = "Year", y = "Health & Wellness Indicator", title = "Health & Wellness", color = "Countries") +
 theme_minimal() +
 theme(axis.text.y = element_text(size = 5))

graph2 <- ggplotly(graph2)
graph2
    
``` 

```{r echo=FALSE}
graph2
``` 

---------------

## Political rights 

---------------

The politics of Norway take place in the framework of a parliamentary, representative democratic constitutional monarchy. Executive power is exercised by the Council of State, the cabinet, led by the Prime Minister of Norway. Legislative power is vested in both the government and the legislature, the Storting, elected within a multi-party system. The judiciary is independent of the executive branch and the legislature.

The Economist Intelligence Unit rated Norway a "full democracy" in 2019. Reporters Without Borders ranked Norway first in the world in the 2019 Press Freedom Index. On March 19, 2020, the Norwegian parliament voted to give the enormous emergency powers to the government. While this is in effect, the government can change any law except for the constitution and human rights legislation. These emergency powers are due to expire in December 2020. During this period Norway is operating with a partially combined executive and legislative branch.

The graph shows that Norway is the best country having regard to political rights. Germany and France are just behind and as a comparison, countries like for example afghanistan or especially South Korea are still far behind.


```{r include=FALSE}
library(spiR)

PRI_1 <- sqs_spi_data(country = c("NOR","DEU","FRA","AFG","PRK"), 
                       year = c("2014","2015","2016", "2017", "2018", "2019"), 
                       indicators = "PRI_1")


```

```{r include=FALSE}

library(ggplot2)
library(plotly)

graph71 <- ggplot(PRI_1) +
 aes(x = var_year, y = value, colour = countryName, group = countryName) +
 geom_line(size = 1.2) +
 scale_color_hue() +
 labs(x = "Year", y = "Political rights indicator", title = "Political rights (0 = no rights / 40 = full rights)", color = "Countries") +
 theme_minimal()

graph81 <- ggplotly(graph71)

```

```{r echo=FALSE}

graph81

```

---------------

# **A pioneering country in terms of ecology**

--------------------

In March 2019, the Norwegian government announced that the world's largest sovereign wealth fund, Norway's, itself funded by petrodollars, will disengage from oil companies in order to reduce the Scandinavian country's economic exposure to oil. If this proposal is dictated by financial rather than environmental considerations, the withdrawal of this major investor is a signal against pollution.

A few months ago, the Norwegian parliament passed a law aimed at achieving a carbon neutral balance by 2030, twenty years earlier than originally planned. It also launched an accelerated programme of greenhouse gas emission reductions, particularly in the oil and gas sector. These emissions could well be totally eliminated in the near future.

---------------

**Summary**

* **Greenhouse gas emission.**

* **Electricity quality.**

---------------

## Greenhouse gas emissions

---------------

Energy-related CO2 emissions in Norway are very low in comparison to other countries. Because the energies used in the country are essentially renewable energies like hydropower. And we can see on the graph below that the majority of the countries are reducing their greenhouse gas emissions which is a great thing for the future. These low emissions are partly explained, for example, by the explosion of electric car sales in the country and the decline in sales of diesel cars for several years now.

For more than twenty-five years, Norway has put in place a set of direct and indirect incentives that are very favorable to the development of electric mobility by applying the "polluter pays" strictly. It is one of the only countries in the world where an electric car is cheaper to buy than its thermal equivalent.

```{r, include=FALSE}

library(spiR)

EQU <- sqs_spi_data(country = c("DNK", "NOR", "NLD", "USA", "FRA"), 
                       year = c("2014","2015","2016", "2017", "2018", "2019"), 
                       indicators = "EQU_2")
EQU
```

```{r, include=FALSE}

library(ggplot2)
library(plotly)

EQU <- EQU[order(EQU$countryName),]

graph6 <- ggplot(EQU, aes(var_year, value, color = countryName)) +
  geom_point(aes(size = 1, frame = var_year)) +
  scale_x_log10() + theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    axis.text.y = element_text(size = 5)) +
    theme(axis.text.y = element_text(size = 7)) + labs(title = "Greenhouse gas emissions") +labs(x = "Year", y = "Emissions CO2 equivalents/GDP") + labs(colour = NULL, size = NULL)

graph7 <- ggplotly(graph6)
graph7

```

```{r echo=FALSE}
graph7
```

---------------

## Electricty Quality 

---------------

Norwegian electricity is almost exclusively produced by its hydropower dams. The country is the 6th largest producer of hydropower in the world in 2018 and the largest in Europe, with 3.3% of the world's hydropower production and 26% of that of the European Union. This is well illustrated with the graph below because Norway is clearly one of the best countries having regard to the electricity quality with other countries like Denemark or Netherlands.

```{r, include=FALSE}

library(spiR)

SHE_2 <- sqs_spi_data(country = c("AUS", "NOR", "USA", "NLD", "DEU", "CAN", "DNK", "FIN"), 
                       year = c("2014","2015","2016", "2017", "2018", "2019"), 
                       indicators = "SHE_2")


SHE_2

```

```{r include=FALSE}

library(ggplot2)
library(plotly)

graph3 <- ggplot(SHE_2) +
 aes(x = var_year, y = value, colour = countryName, group = countryName) +
 geom_line(size = 1.2) +
 scale_color_hue() +
 labs(x = "Year", y = "Electricity Quality Indicator", title = "Electricity Quality", color = "Countries") +
 theme_minimal() 

graph31 <- ggplotly(graph3)
graph31

```

```{r echo=FALSE}
graph31
```

---------------

# **An unevenly distributed population**

--------------------

Norway has a population of about 5 million, a figure that is growing by 1.3% per year. The population occupies the lower regions with the most fertile soils, suitable for agriculture and forest expansion.The share of the rural population has steadily decreased since the last century, while the urban population has grown very rapidly.  

Moreover, immigration in recent years has accounted for more than half of the population growth. Internal migration has thus changed the population distribution from the north of the country, Sørland and Trøndelag to the Oslo region and Østland. The metropolitan area of Oslo, the capital city, has almost 16% of the population. 

---------------

**Summary**

* **Density Map.**

* **Norway's density forecast.**

* **Migration Map.**

* **Norway's population forecast.**

---------------

## Density Map

---------------

This map highlights the great disparity that exists on the Norwegian territory in terms of Density. Indeed, one notices immediately that the vast majority of the country is very sparsely populated. Most regions have a Density of less than 20 inhabitants per km². By way of comparison, the average Density in France is about 117 inhabitants per km² compared to 13 in Norway. 

```{r warning=FALSE, include=FALSE}
library(sf)
library(ggplot2)
library(tmap)
library(tmaptools)
library(leaflet)
library(dplyr)

mydata <- readr::read_csv("Density Map/Density per Fylker.csv")

mymap <- st_read("Density Map/NORWAY SHAPE/NOR_adm1.shp", stringsAsFactors = FALSE)

datamap1 <- inner_join(mymap, mydata) 

datamap2 <- ifelse(datamap1$Density >= 0 & datamap1$Density <= 5, "0 to 5", ifelse(datamap1$Density >= 6 & datamap1$Density <= 10, "6 to 10", ifelse(datamap1$Density >= 11 & datamap1$Density <= 20, "11 to 20", ifelse(datamap1$Density >= 21 & datamap1$Density <= 50, "21 to 50", ifelse(datamap1$Density >= 51 & datamap1$Density <= 100, "51 to 100", ifelse(datamap1$Density >= 101 & datamap1$Density <= 200, "101 to 200", ifelse(datamap1$Density >= 201 & datamap1$Density <= 500, "201 to 500", ifelse(datamap1$Density >= 501, "501 or more", NA))))))))

cut(datamap1$Density, breaks=c(0, 5, 10, 20, 50, 100, 200, 500, Inf), labels=c("0 to 5", "6 to 10", "11 to 20", "21 to 50", "51 to 100", "101 to 200","201 to 500", "500 or more"))

mylabels <- c("0 to 5", "6 to 10", "11 to 20", "21 to 50", "51 to 100", "101 to 200", "201 to 500", "500 or more")  

```

```{r warning=FALSE, include=FALSE}

datamap1$Density <- base::cut(datamap1$Density,
                        breaks = c(0, 5, 10, 20, 50, 100, 200, 500, 2000), 
                        labels = mylabels, right = F, ordered_result = T)

```

```{r include=FALSE}

tm_shape(datamap1) +
  tm_polygons("Density", id = "NAME_1", palette = "Oranges")+ "Density"
  theme_minimal()

tmap_mode("view")
DensityMap <- tmap_last()

```

```{r echo=FALSE, warning=FALSE}

DensityMap

#tmap_save(DensityMap, "DensityMap.html")

```

---------------

## Norway's Density Forecast

---------------

Norway is averaging a density of 13 individuals per km², making Norway only the 171st most densely populated country on the planet. With slightly over 80% of the population living in or around major cities, it is safe to say that Norway is a fairly urban country which is slowly getting more dense. According to this projective graph, Norway's density should be around 17.75 in 2050. And with a confidence level of 80% we can say that the density will be between 15.88 and 19.62 in 2050.

```{r include=FALSE}

library(readxl)
library(forecast)
library(autoplotly)
library(plotly)

DensityPerYear <- read_xlsx("DensityPerYear.xlsx")

tsDensityPerYear <- ts(DensityPerYear$Density, frequency = 1, start = c(1970))

autoarima1 <- auto.arima(tsDensityPerYear)

forecast1 <- forecast(autoarima1, h=32)

#p <- autoplot(forecast1)
p <- autoplotly(forecast1)
q <- p +
  ggplot2::ggtitle("Norway's density expectations") +
  ggplot2::labs(y = "Density", x = "Year")

```

```{r echo=FALSE}

q

```

---------------

## Migration Map

---------------

This map shows the different migration rates that exists in the different Norwegian regions. We can see that there is a polarization around the city of Oslo which represents the economical center of Norway. Regions in the North are for the majority having less attraction than South regions but we can see that only one region has a negative migration rate : Rogaland. This is a great thing because it is the proof that Norway is an attractive country for people. 

```{r warning=FALSE, include=FALSE}

library(sf)
library(ggplot2)
library(tmap)
library(tmaptools)
library(leaflet)
library(dplyr)

mydatabisbis <- readr::read_csv("Migration Map/MigrationRateperFylker.csv")

mymapbisbis <- st_read("Migration Map/NORWAY SHAPE BIS BIS/NOR_adm1.shp", stringsAsFactors = FALSE)

datamap1bisbis <- inner_join(mymapbisbis, mydatabisbis) 


```

```{r warning=FALSE, include=FALSE}

tm_shape(datamap1bisbis) +
  tm_polygons("Net migration rate, %", id = "NAME_1", palette = "Blues")+ "Net migration rate, %"
  theme_minimal()
  
tmap_mode("view")
MigrationMap <- tmap_last()

```

```{r echo=FALSE, warning=FALSE}

MigrationMap

```

---------------

## Norway's population forecast

---------------

This projective graph shows that we can expect Norway's population to keep growing over years. As an example by 2050 the population of Norway is expected to increase by around 1 million people.

```{r include=FALSE, echo = FALSE}

library(readxl)
library(forecast)
library(autoplotly)
library(plotly)

PopulationPerYear <- read_xlsx("PopulationPerYear.xlsx")

tsPopulationPerYear <- ts(PopulationPerYear$Population, frequency = 0.2, start = c(1955))

autoarima1 <- auto.arima(tsPopulationPerYear)

forecast1 <- forecast(autoarima1, h=6)

#p2 <- autoplot(forecast1)
p2 <- autoplotly(forecast1)
q2 <- p2 +
  ggplot2::ggtitle("Norway's population expectations") +
  ggplot2::labs(y = "Population", x = "Year")

```

```{r echo=FALSE}

q2

```


---------------

# **Conclusion**

--------------------

Economically, Norway is a pretty stable country which has different leading sectors. But the country still very dependent of its Oil and Gas development which represents about 20% of its economy. The country has a positive trade balance, so even if the GDP is unevenly divided between the regions it shows the economical health of the country. Moreover the country has some great scores in what concerns economic freedom even if the government's budget is structured around the state-owned oil and gas company Equinor. Socially, Norway is an exemplary country. Well-being is abundant and the health system is working perfectly. On top of that there is very few unemployment in the country and Norway is the best country in the world in regards to political rights.

Environmentally the country is really advanced with very few greenhouse gas emission in comparison to other developed countries and with an incredible average electricity quality which is due to the fact that the country is running almost exclusively with hydro power. However, the fact that the country's economy is relying on oil and gas exportation is a real downside which needs to be considered regarding the environmental aspect.

Finally demographically, Norway is a country which has a population that is still growing and that has a very low density in comparison to many countries of the same size. The territory of the country is also very sparsely populated which creates a polarization around the south and especially around the capital city Oslo.




